Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/draft.tex
ratios in results2
Update draft.tex

We show that the simulation results are consistent with predictions of the R2B2 open-source library for ballot polling audits. Because the \Minerva round schedule needs to be predetermined, we observe that the simulator is useful as a tool for understanding the behavior of \Minerva with the fixed round schedule. Most importantly, we observe that both \BRAVO audits are more conservative than needed, while \Minerva audits stop with fewer ballots, for both first round stopping probabilities, though using \Minerva is not as advantageous for the smaller first round stopping probability.

@@

\section{Software}
\label{sec:software}
\input{sections/03-software}

>>>>

We show that the simulation results are consistent with predictions of the R2B2 open-source library for ballot polling audits. Because the \Minerva round schedule needs to be predetermined, we observe that the simulator is useful as a tool for understanding the behavior of \Minerva with the fixed round schedule. Most importantly, we observe that both \BRAVO audits are more conservative than needed, while \Minerva audits stop with fewer ballots, for both first round stopping probabilities. However, the advantage of using \Minerva decreases considerably for the smaller first round stopping probability, as one would expect.

@@

%\section{Software}
%\label{sec:software}
%\input{sections/03-software}
